% 参考文献

% \bibitem{bib:epaper}					% 和文著書の例
% Author():
% 	'' ,''
% 	{\it  }
% 	, pp.~--, .

%\begin{thebibliography}{99}			% 参考文献数が二桁の場合
\begin{thebibliography}{9}				% 参考文献数が一桁の場合

	\bibitem{bib:epaper}					% 和文著書の例
	Author(V. Ferrari, T. Tuytelaars, and L. Van Gool):
		''Simultaneous object recognition and segmentation from single or multiple model views,''
		{\it International Journal of Computer Vi-sion}
		,vol.67, no.2, pp.~159--188, 2006.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(A. Collet, M. Martinez, and S. S. Srinivasa):
		'' The moped framework: Object recognition and pose estimation for manipulation,''
		{\it The International Journal of Robotics Re-search }
		,vol.30, no.10, pp.~1284--1306, 2011.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(M. Aubry, D. Maturana, A. A. Efros, B. C. Russell, and J. Sivic):
		'' Seeing 3d chairs: Exemplar part-based 2d-3d align- ment using a large dataset of cad models,''
		{\it  in Proceed- ings of the IEEE Computer Vision and Pattern Recognition (CVPR)}
		, pp.~3762--3769, 2014.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(M. A. Fischler and R. C. Bolles):
		'' Random sample consen- sus: A paradigm for model fitting with applications to image analysis and automated cartography,''
		{\it Communications of the ACM}
		,vol.24m no.6, pp.~381--395, 1981.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(S. Tulsiani and J. Malik):
		'' Viewpoints and keypoints,''
		{\it in Proceedings of the IEEE Computer Vision and Pattern Recognition (CVPR)}
		, pp.~1510--1519, 2015.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(M. Schwarz, H. Schulz, and S. Behnke):
		'' Rgb-d object recognition and pose estimation based on pre-trained convolutional neural network features,''
		{\it  in Robotics and Au- tomation (ICRA), 2015 IEEE International Conference on, IEEE}
		, pp.~1329--1335, 2015.
	

	\bibitem{bib:epaper}					% 和文著書の例
	Author(Guilhem Cheron, Ivan Laptev, Cordelia Schmid):
		'' P-CNN: Pose-Based CNN Features for Action Recognition,''
		{\it Proceedings of the IEEE International Conference on Computer Vision (ICCV)}
		, pp.~3218--3226, 2015.

	% 凡例
	\bibitem{bib:epaper}					% 和文著書の例
		Author(WANG, Chen):
			''Densefusion: 6d object pose estimation by iterative dense fusion,''
			{\it Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR)}
			, pp.~3343--3352, 2019.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(LIU Yuan):
		''Gen6D: Generalizable model-free 6-DoF object pose estimation from RGB images,''
		{\it In: Computer Vision–ECCV 2022: 17th European Conference}
		, pp.~298--315, 2022.
			
	\bibitem{bib:epaper}					% 和文著書の例
	Author(REDMON, Joseph; FARHADI, Ali):
		''Yolov3: An incremental improvement,''
		{\it In: Computer Vision–ECCV 2022: 17th European Conference}
		, 2018.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(FISHER, Alex):
		''ColMap: A memory-efficient occupancy grid mapping framework,''
		{\it Robotics and Autonomous Systems}
		, 2021.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(GIRSHICK, Ross):
		''Fast r-cnn,''
		{\it In: Proceedings of the IEEE international conference on computer vision}
		, pp.~1440--1448, 2015.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(Xian, Yongqin and Choudhury, Subhabrata and He, Yang and Schiele, Bernt and Akata, Zeynep):
		''Semantic Projection Network for Zero- and Few-Label Semantic Segmentation,''
		{\it The IEEE Conference on Computer Vision and Pattern Recognition (CVPR)}
		, pp.~8256--8265, 2019.

	\bibitem{bib:epaper}					% 和文著書の例
	Author(ZHOU, Tao):
		''RGB-D salient object detection: A survey,''
		{\it Computational Visual Media}
		, 7; 37-69, 2021.


\end{thebibliography}
